\begin{thebibliography}{99}

\bibitem{Asmussen} Asmussen, S. (1987). \textit{Applied Probability and Queues}. John Wiley and Sons.

\bibitem{Bhat} Bhat, N. (2008). \textit{An Introduction to Queueing Theory: Modelling and Analysis in Applications}. Birkhauser.

\bibitem{Boxma} Boxma, J. O. (1987). Pseudoconservation Laws in Cyclic Service Systems. \textit{Journal of Applied Probability}, 24, 949-964.

\bibitem{Borovkov} Borovkov, A. A., and Schassberger, R. (1995). Ergodicity of a Polling Network. \textit{Stochastic Processes and their Applications}, 50(2), 253-262.

\bibitem{BosBoon} van den Bos, L., and Boon, M. (2013). \textit{Networks of Polling Systems} (report). Eindhoven University of Technology.

\bibitem{BoonMeiWinands} Boon, M. A. A., van der Mei, R. D., and Winands, E. M. M. (2011). Applications of Polling Systems. February 24, 2011.

\bibitem{HookHee} Ng, C. H., and Soong, B. H. (2008). \textit{Queueing Modelling Fundamentals with Applications in Communications Networks}. John Wiley and Sons.

\bibitem{Chen} Chen, H. (1995). Fluid Approximations and Stability of Multiclass Queueing Networks I: Work-conserving Disciplines. \textit{Annals of Applied Probability}.

\bibitem{CooperII} Cooper, R. B. (1970). Queues Served in Cyclic Order: Waiting Times. \textit{The Bell System Technical Journal}, 49, 399-413.

\bibitem{Dai} Dai, J. G. (1995). On Positive Harris Recurrence of Multiclass Queueing Networks: A Unified Approach Via Fluid Limit Models. \textit{The Annals of Applied Probability}, 5(1), 49-77.

\bibitem{DaiSean} Dai, J. G., and Meyn, S. P. (1995). Stability and Convergence of Moments for Multiclass Queueing Networks Via Fluid Limit Models. \textit{IEEE Transactions on Automatic Control}, 40(11), 1889-1904.

\bibitem{DaiWeiss} Dai, J. G., and Weiss, G. (1996). Stability and Instability of Fluid Models for Reentrant Lines. \textit{Mathematics of Operations Research}, 21(1), 115-134.

\bibitem{Daley68} Daley, D. J. (1968). The Correlation Structure of the Output Process of Some Single Server Queueing Systems. \textit{The Annals of Mathematical Statistics}, 39(3), 1007-1019.

\bibitem{Davis} Davis, M. H. A. (1984). Piecewise Deterministic Markov Processes: A General Class of Nondiffusion Stochastic Models. \textit{Journal of the Royal Statistical Society, Series B}, 46(3), 353-388.

\bibitem{Down} Down, D. (1998). On the Stability of Polling Models with Multiple Servers. \textit{Journal of Applied Probability}, 35(3), 925-935.

\bibitem{Disney} Disney, R. L., Farrell, R. L., and Morais, P. R. (1973). A Characterization of $M/G/1$ Queues with Renewal Departure Processes. \textit{Management Science}, 19(11), Theory Series, 1222-1228.

\bibitem{Eisenberg} Eisenberg, M. (1972). Queues with Periodic Service and Changeover Time. \textit{Operations Research}, 20(2), 440-451.

\bibitem{FrickerJaibi} Fricker, C., and Jaïbi, M. R. (1994). Monotonicity and Stability of Periodic Polling Models. \textit{Queueing Systems}, 15(1-4), 211-238.

\bibitem{Getoor} Getoor, R. K. (1979). Transience and Recurrence of Markov Processes. In J. Azema and M. Yor (Eds.), \textit{Seminaire de Probabilités XIV} (pp. 397-409). New York: Springer-Verlag.

\bibitem{Gut} Gut, A. (1995). \textit{Stopped Random Walks: Limit Theorems and Applications}. Applied Probability.

\bibitem{KaspiMandelbaum} Kaspi, H., and Mandelbaum, A. (1992). Regenerative Closed Queueing Networks. \textit{Stochastics: An International Journal of Probability and Stochastic Processes}, 39(4), 239-258.

\bibitem{Kleinrock} Kleinrock, L. (1975). \textit{Queueing Systems: Theory, Volume 1}. Wiley-Interscience.

\bibitem{Konheim} Konheim, A. G., Levy, H., and Srinivasan, M. M. (1994). Descendant Set: An Efficient Approach for the Analysis of Polling Systems. \textit{IEEE Transactions on Communications}, 42(2-4), 1245-1253.

\bibitem{Lang} Lang, S. (1973). \textit{Calculus of Several Variables}. Addison-Wesley Publishing Company.

\bibitem{LevySidi} Levy, H., and Sidi, M. (1990). Polling Systems: Applications, Modeling, and Optimization. \textit{IEEE Transactions on Communications}, 30(10), 1750-1760.

\bibitem{Stability} Fricker, C., and Jaïbi, M. R. (1998). Stability of Multi-server Polling Models. Institute National de Recherche en Informatique et en Automatique.

\bibitem{MeynTweedie2} Meyn, S. P., and Tweedie, R. L. (1993). \textit{Markov Chains and Stochastic Stability}. Springer-Verlag.

\bibitem{MeynDown} Meyn, S. P., and Down, D. (1994). Stability of Generalized Jackson Networks. \textit{The Annals of Applied Probability}.

\bibitem{MeiBorst} van der Mei, R. D., and Borst, S. C. (1997). Analysis of Multiple-server Polling Systems by Means of the Power-Series Algorithm. \textit{Stochastic Models}, 13(2), 339-369.

\bibitem{Meyn2} Meyn, S. P. (1995). Transience of Multiclass Queueing Networks via Fluid Limit Models. \textit{The Annals of Applied Probability}, 5(4), 946-957.

\bibitem{Rouche} Adan, I. J. B. F., van Leeuwaarden, J. S. H., and Winands, E. M. M. (2006). On the Application of Rouche’s Theorem in Queueing Theory. \textit{Operations Research Letters}, 34(3), 355-360.

\bibitem{TesisRoubos} Roubos, A. (2007). \textit{Polling Systems and their Applications}. Vrije Universiteit Amsterdam.

\bibitem{RepTec} Saavedra, B. P. (2011). Informe Técnico del Microsimulador. Departamento de Matemáticas.

\bibitem{Semenova} Vishnevskii, V. M., and Semenova, O. V. (2006). Mathematical Methods to Study the Polling Systems. \textit{Automation and Remote Control}, 67(2), 173-220.

\bibitem{Serfozo} Serfozo, R. (2009). \textit{Basics of Applied Stochastic Processes}. Springer-Verlag.

\bibitem{Sharpe} Sharpe, M. (1998). \textit{General Theory of Markov Processes}. Academic.

\bibitem{Sigma} Sigman, K. (1990). The Stability of Open Queueing Networks. \textit{Stochastic Processes and their Applications}, 35(1), 11-15.

\bibitem{SidiLevy1} Sidi, M., and Levy, H. (1990). Customer Routing in Polling Systems. In P. King, I. Mitrani, and R. Pooley (Eds.), \textit{Proceedings Performance '90}. North-Holland, Amsterdam.

\bibitem{SidiLevy2} Sidi, M., and Levy, H. (1991). Polling Systems with Simultaneous Arrivals. \textit{IEEE Transactions on Communications}, 39(6), 823-827.

\bibitem{Sigman2} Sigman, K., Thorisson, H., and Wolff, R. W. (1994). A Note on the Existence of Regeneration Times. \textit{Journal of Applied Probability}, 31, 1116-1122.

\bibitem{Stidham} Stidham, S. Jr. (1972). Regenerative Processes in the Theory of Queues, with Applications to the Alternating Priority Queue. \textit{Advances in Applied Probability}, 4(3), 542-577.

\bibitem{Takagi} Takagi, H. (1986). \textit{Analysis of Polling Systems}. Cambridge: MIT Press.

\bibitem{TakagiI} Takagi, H., and Kleinrock. (1986). Analysis of Polling Systems. Cambridge: MIT Press.

\bibitem{TakagiII} Takagi, H. (1988). Queueing Analysis of Polling Models. \textit{ACM Computing Surveys}, 20(1), 5-28.

\bibitem{Thorisson} Thorisson, H. (2000). \textit{Coupling, Stationarity, and Regeneration}. Probability and its Applications. Springer-Verlag.

\bibitem{Winands} Winands, E. M. M., Adan, I. J. B. F., and van Houtum, G. J. (2006). Mean Value Analysis for Polling Systems. \textit{Queueing Systems}, 54, 35-44.

\bibitem{ISL} James, G., Witten, D., Hastie, T., and Tibshirani, R. (2013). \textit{An Introduction to Statistical Learning: with Applications in R}. Springer.

\bibitem{Logistic} Hosmer, D. W., Lemeshow, S., and Sturdivant, R. X. (2013). \textit{Applied Logistic Regression} (3rd ed.). Wiley.

\bibitem{PatternRecognition} Bishop, C. M. (2006). \textit{Pattern Recognition and Machine Learning}. Springer.

\bibitem{Harrell} Harrell, F. E. (2015). \textit{Regression Modeling Strategies: With Applications to Linear Models, Logistic and Ordinal Regression, and Survival Analysis}. Springer.

\bibitem{RDocumentation} R Documentation and Tutorials: \url{https://cran.r-project.org/manuals.html}

\bibitem{RBlogger} Tutorials on R-bloggers: \url{https://www.r-bloggers.com/}

\bibitem{CourseraML} Coursera: \textit{Machine Learning} by Andrew Ng.

\bibitem{edXDS} edX: \textit{Data Science and Machine Learning Essentials} by Microsoft.

\bibitem{Ross} Ross, S. M. (2014). \textit{Introduction to Probability and Statistics for Engineers and Scientists}. Academic Press.

\bibitem{DeGroot} DeGroot, M. H., and Schervish, M. J. (2012). \textit{Probability and Statistics} (4th ed.). Pearson.

\bibitem{Hogg} Hogg, R. V., McKean, J., and Craig, A. T. (2019). \textit{Introduction to Mathematical Statistics} (8th ed.). Pearson.

\bibitem{Kleinbaum} Kleinbaum, D. G., and Klein, M. (2010). \textit{Logistic Regression: A Self-Learning Text} (3rd ed.). Springer.

\bibitem{Wasserman} Wasserman, L. (2004). \textit{All of Statistics: A Concise Course in Statistical Inference}. Springer.

\bibitem{KhanAcademy} Probability and Statistics Tutorials on Khan Academy: \url{https://www.khanacademy.org/math/statistics-probability}

\bibitem{OnlineStatBook} Online Statistics Education: \url{http://onlinestatbook.com/}

\bibitem{Peng} Peng, C. Y. J., Lee, K. L., and Ingersoll, G. M. (2002). \textit{An Introduction to Logistic Regression Analysis and Reporting}. The Journal of Educational Research.

\bibitem{Agresti} Agresti, A. (2007). \textit{An Introduction to Categorical Data Analysis} (2nd ed.). Wiley.

\bibitem{Han} Han, J., Pei, J., and Kamber, M. (2011). \textit{Data Mining: Concepts and Techniques}. Morgan Kaufmann.

\bibitem{TowardsDataScience} Data Cleaning and Preprocessing on Towards Data Science: \url{https://towardsdatascience.com/data-cleaning-and-preprocessing}

\bibitem{Molinaro} Molinaro, A. M., Simon, R., and Pfeiffer, R. M. (2005). \textit{Prediction Error Estimation: A Comparison of Resampling Methods}. Bioinformatics.

\bibitem{EvaluatingModels} Evaluating Machine Learning Models on Towards Data Science: \url{https://towardsdatascience.com/evaluating-machine-learning-models}

\bibitem{LogisticRegressionGuide} Practical Guide to Logistic Regression in R on Towards Data Science: \url{https://towardsdatascience.com/practical-guide-to-logistic-regression-in-r}

\bibitem{CourseraStatistics} Coursera: \textit{Statistics with R} by Duke University.

\bibitem{edXProbability} edX: \textit{Data Science: Probability} by Harvard University.

\bibitem{CourseraLogistic} Coursera: \textit{Logistic Regression} by Stanford University.

\bibitem{edXInference} edX: \textit{Data Science: Inference and Modeling} by Harvard University.

\bibitem{CourseraWrangling} Coursera: \textit{Data Science: Wrangling and Cleaning} by Johns Hopkins University.

\bibitem{edXRBasics} edX: \textit{Data Science: R Basics} by Harvard University.

\bibitem{CourseraRegression} Coursera: \textit{Regression Models} by Johns Hopkins University.

\bibitem{edXStatInference} edX: \textit{Data Science: Statistical Inference} by Harvard University.

\bibitem{SurvivalAnalysis} An Introduction to Survival Analysis on Towards Data Science: \url{https://towardsdatascience.com/an-introduction-to-survival-analysis}

\bibitem{MultinomialLogistic} Multinomial Logistic Regression on DataCamp: \url{https://www.datacamp.com/community/tutorials/multinomial-logistic-regression-R}

\bibitem{CourseraSurvival} Coursera: \textit{Survival Analysis} by Johns Hopkins University.

\bibitem{edXHighthroughput} edX: \textit{Data Science: Statistical Inference and Modeling for High-throughput Experiments} by Harvard University.

\bibitem{Sigman1} Sigman, K., and Wolff, R. W. (1993). A Review of Regenerative Processes. \textit{SIAM Review}, 38(2), 269-288.

%__________________________________________________________________________________________________________________
% A
%__________________________________________________________________________________________________________________
\bibitem{Rouche} I.J.B.F. Adan, J.S.H. van Leeuwaarden, and E.M.M. Winands. On the application of Rouches theorem in queueing theory. Operations Research Letters, 34(3):355-360, 2006.


\bibitem{Asmussen} Asmussen Soren, Applied Probability and
Queues, John Wiley and Sons, 1987.%[1]
%__________________________________________________________________________________________________________________
% B
%__________________________________________________________________________________________________________________

\bibitem{Bhat} Bhat Narayan, An Introduction to Queueing Theory
Modelling and Analysis in Applications, Birkhauser, 2008.

\bibitem{Boxma} Boxma J. O., Analysis and Optimization of Polling
Systems, Queueing, Performance and Control in ATM, pp. 173-183,
1991.

\bibitem{Boxma2} Boxma J. O., Pseudoconservation Laws in Cyclic
Service Systems, Journal of Applied Probability, vol. 24, 1987,
pp. 949-964.

\bibitem{BoonMeiWinands} Boon M.A.A., Van der Mei R.D.  and
Winands E.M.M., Applications of Polling Systems, 2011.

\bibitem{Borovkov} Borovkov. A. A. and Schassberger R., Ergodicity
of a Polling Network, Stochastic Processes and their Applications,
vol. 50, no. 2, 1995, pp. 253-262.


\bibitem{BosBoon}Laurent van den Bos and Marko Boon, Networks of Polling Systems (report), Eindhoven University of Technology, 2013.

\


%__________________________________________________________________________________________________________________
% C 
%__________________________________________________________________________________________________________________
\bibitem{HookHee} Chee-Hook Ng. y Boon-Hee Soong, Queueing
Modelling Fundemantals with Applications in Communications
Networks, John-Wiley and Sons, Ltd, 2008.

\bibitem{Chen} Chen H., Fluid Approximations and Stability of
Multiclass Queueing Networks I: Work-Conserving Disciplines,
Annals Applied Probabability, vol. 5, no. 3, 1995, pp. 637-665.

\bibitem{CooperI} R.B. Cooper, G. Murray, Queues served in cyclic order (The Bell
System Technical Journal, 48 (1969) 675-689).

\bibitem{CooperII} R.B. Cooper, Queues served in cyclic order: waiting times (The
Bell System Technical Journal, 49 (1970) 399-413).

%__________________________________________________________________________________________________________________
% D
%__________________________________________________________________________________________________________________
\bibitem{Dai} Dai Jean G., On positive Harris Recurrence of Multiclass Queueing
Networks: A Unified Approach Via Fluid Limit Models, The Annals of
Applied Probability, vol. 5, No. 1, 1995, pp. 49-77.

\bibitem{DaiSean} Dai Jim G. and Meyn Sean P., Stability and Convergence of Moments
for Multiclass Queueing Networks via Fluid Limit Models, IEEE
transactions on Automatic Control, vol. 40, No. 11, 1995, pp.
1889-1904.

\bibitem{DaiWeiss}
Dai Jim G.  and Weiss G., Stability and Inestability of Fluid
Models for Reentrant Lines, Mathematics of Operation Research,
vol. 21, no. 1, 1996, pp. 115-134.

\bibitem{Daley68} D.J. Daley, The correlation structure of the output process of
 some single server queueing systems, The Annals of Mathematical Statistics, Vol. 39. No. 3, pp. 1007-1019, 1968.

\bibitem{Davis} Davis, M. H. A., Piecewise Deterministic Markov
Processes: A General Class of Nondifussion Stochastic Models.
Journal of Royal Statistics Society Serie B, vol. 46, no. 3, 1984,
pp. 353-388.

\bibitem{Down} Down D., On the Stability of Polling Models with Multiple Servers,
Journal of Applied Probability, vol. 35, no. 3, 1998, pp. 925-935.

\bibitem{Daley68} D.J. Daley, The correlation structure of the output process of  some single server queueing systems, The Annals of Mathematical Statistics, Vol. 39. No. 3, pp. 1007-1019, 1968. 

\bibitem{Disney} Ralpjh L. Disney, Robert L. Farrell and Paulo Renato Morais, A Characterization of $M/G/1$ Queues with Renewal Departure Processes,  Manage of Science, Vol. 19, No. 11, Theory Series, pp. 1222-1228, 1973.

%__________________________________________________________________________________________________________________
% E
%__________________________________________________________________________________________________________________
\bibitem{Eisenberg} M. Eisenberg, Queues with periodic service and changeover time
(Operations Research, 20 (2)(1972) 440-451).

%__________________________________________________________________________________________________________________
% F
%__________________________________________________________________________________________________________________

\bibitem{FrickerJaibi}
Fricker Christine and Ja{\"\i}bi M.R., Monotonicity and Stability
of Periodic Polling Models,  Queueing Systems, vol. 15, no. 1-4,
1994, pp. 211-238.

\bibitem{Stability}
Fricker Christine and Ja{\"\i}bi M.R., Stability of Multi-Server
Polling Models, Institute National de Recherche en Informatique et
en Automatique, Issue 3347, 1998.

%__________________________________________________________________________________________________________________
% G
%__________________________________________________________________________________________________________________

\bibitem{Getoor} Getoor R. K., Transience and recurrence of
Markov processes, Siminaire de Probabilitis XIV, J. Azema and M
Yor, Eds. New York Springer-Verlag, 1979.

\bibitem{Gut} Gut A., Stopped Random Walks: Limit Theorems and
Applications, Applied Probability, 1995.

%__________________________________________________________________________________________________________________
% H
%__________________________________________________________________________________________________________________

\bibitem{HookHee} Chee-Hook Ng. y Boon-Hee Soong, Queueing
Modelling Fundemantals with Applications in Communications
Networks, John-Wiley and Sons, Ltd, 2008.

%__________________________________________________________________________________________________________________
% I
%__________________________________________________________________________________________________________________

%__________________________________________________________________________________________________________________
% J
%__________________________________________________________________________________________________________________

%__________________________________________________________________________________________________________________
% K
%__________________________________________________________________________________________________________________
\bibitem{KaspiMandelbaum} Kaspi H. and Mandelbaum A., Regenerative Closed Queueing
Networks, Stochastics: An International Journal of Probability and
Stochastic Processes, vol. 39, no. 4, 1992, pp. 239-258.

\bibitem{Konheim} A.G. Konheim, H. Levy, M.M. Srinivasan, Descendant set: an efficient
approach for the analysis of polling systems (IEEE Transactions
on Communications, 42 (2/3/4)(1994) 1245-1253).

\bibitem{Kleinrock} Leonard Kleinrock, Theory, Volume 1, Queueing Systems Wiley-Interscience, 1975,


\bibitem{Konheim} A. G. Konheim, h. Levy and M. M. Srinivasan. Descendant set: an efficient approach for the analysis of polling systems. IEEE Trabsanctions on Communications, 42(2-4): pp. 1245-1253, 1994.


%__________________________________________________________________________________________________________________
% L
%__________________________________________________________________________________________________________________

\bibitem{Lang} Serge Lang, Calculus of Several Variables, Addison-Wesley Publishing Company, 1973.

\bibitem{LevySidi}
Levy Hanoch y Sidi Moshe , Polling Systems: Applications, Modeling, and Optimization, IEEE Transactions on Communications, vol. 30, no. 10, 1990, pp. 1750-1760.


%__________________________________________________________________________________________________________________
% M
%__________________________________________________________________________________________________________________
\bibitem{MeiBorst} van der Mei, R.D. and Borst, S. C., Analysis of Multiple-Server Polling
Systems by Means of the Power-Series Algorithm, Stochastic Models,
vol. 13, no. 2, 1997, pp. 339-369.


\bibitem{Meyn} Meyn Sean P., Transience of Multiclass Queueing Networks via Fluid
Limit Models, The Annals of Applied Probability, vol. 5, no. 4,
1995, pp.946-957.

\bibitem{MeynTweedie} Meyn S. P. and Tweedie R. L., Stability of Markovian Processes
 II:Continuous Time Processes and Sample Chains, Advanced Applied Pobability, vol. 25, 1993, pp. 487-517.
\bibitem{MeynTweedie2} Meyn S. P. and Tweedie R. L., Markov Chains and Stochastic Stability,
1993.

\bibitem{MeynDown} Meyn, S.P. and Down, D., Stability of Generalized Jackson
Networks, The Annals of Applied Probability, 1994.


%__________________________________________________________________________________________________________________
% N
%__________________________________________________________________________________________________________________
%__________________________________________________________________________________________________________________
% O
%__________________________________________________________________________________________________________________
%__________________________________________________________________________________________________________________
% P
%__________________________________________________________________________________________________________________
%__________________________________________________________________________________________________________________
% Q
%__________________________________________________________________________________________________________________
%__________________________________________________________________________________________________________________
% R
%__________________________________________________________________________________________________________________

\bibitem{TesisRoubos}
Roubos Alex, Polling Systems and their Applications, Vrije
Universiteit Amsterdam, 2007.

%\bibitem{Rouche} I.J.B.F. Adan, J.S.H. van Leeuwaarden and E.M.M. Winands, On the application of Rouche?s theorem in queueing theory, Operation Research Letters, Vol. 34, Issue 3, pp. 355-360, 2006. EURANDOM


%__________________________________________________________________________________________________________________
% S
%__________________________________________________________________________________________________________________
\bibitem{RepTec}
Saavedra B. P., Informe T\'ecnico del Microsimulador, Departamento
de Matem\'atias, 2011.

\bibitem{Semenova}
Vishnevskii V.M. and Semenova O.V., Mathematical Methods to Study the Polling Systems, Automation and Remote Control, vol. 67, no. 2, 2006, pp. 173-220.

\bibitem{Serfozo} Richard Serfozo, Basics of Applied Stochastic Processes, Springer-Verlag, 2009.


\bibitem{Sharpe} Sharpe Michael , General Theory of Markov Processes. Boston, M.A.
Academic, 1998.


\bibitem{Sigma} Sigman Karl, The Stability of Open Queueing
Networks, Stochastic Processes and their Applications, vol. 35,
no. 1, 1990, pp. 11-15.

\bibitem{SidiLevy1} Sidi M.  and Levy H.,  Customer Routing in Polling Systems, In: P. King, I. Mitrani, and R. Pooley (Eds.), Proceedings
Performance '90, North-Holland, Amsterdam, 1990.


\bibitem{SidiLevy2} Sidi M.  and Levy H., Polling Systems with Simultaneus Arrivals. IEEE Transactions on Communications, vol. 39, no. 6, 1991, pp.
823-827.

\bibitem{Sigman2} Karl Sigman, Hermann Thorisson and Ronald W. Wolff, A Note on the Existence of Regeneration Times, Journal of Applied Probability, vol. 31, pp. 1116-1122, 1994.



\bibitem{Stidham} Shaler Stidham, Jr., Regenerative Processes in the theory ow queues, with applications to the alternating priority queue, Advances in Applied Probability,  Vol. 4, no. 3, 1972,pp. 542-577.


%__________________________________________________________________________________________________________________
% T
%__________________________________________________________________________________________________________________

\bibitem{234} Takagi H., Analysis of Polling Systems, Cambdrige: MIT Press, 1986
\bibitem{TakagiI} Takagi H. and Kleinrock, Analysis of Polling Systems, Cambdrige:
MIT Press, 1986
\bibitem{Takagi}Takagi Hideaki, Queueing Analysis of Polling Models, ACM computing Surveys, vol. 20, no. 1, 1988, pp. 5-28.
\bibitem{Thorisson} Hermann Thorisson, Coupling, Stationarity, and Regeneration, Probability and its Applications, Springer-Verlag, 2000.
%__________________________________________________________________________________________________________________
% U
%__________________________________________________________________________________________________________________
%__________________________________________________________________________________________________________________
% V
%__________________________________________________________________________________________________________________
%__________________________________________________________________________________________________________________
% W
%__________________________________________________________________________________________________________________
\bibitem{Winands} E.M.M. Winands, I.J.B.F. Adan adn G.J. van Houtum, Mean value analysis for polling systems,
Queueing Systems (2006), 54:35-44,
%__________________________________________________________________________________________________________________
% X
%__________________________________________________________________________________________________________________
%__________________________________________________________________________________________________________________
% Y
%__________________________________________________________________________________________________________________
%__________________________________________________________________________________________________________________
% Z
%__________________________________________________________________________________________________________________



\bibitem{166} Konheim, A.G. and Meister, B., Waiting Lines and Times in a System with Polling, J. ACM, 1974, vol. 21, n0. 3, pp. 470-490.

\bibitem{191}
Levy, H. and Kleinrock, L., Polling Systems with Zero Switch-over Periods: A General Method for Analysis the Expected DElay, Performance Evaluat., 1991, vol. 13, no. 2, pp. 97-107.


\bibitem{269} Yechiali, U., Analysis and Control of Polling
systems, in Performance Evaluation of Computer and Communications
Systems, Donatiello, L. and Nelson R., Eds. Berlin: Springer
Verlag, 1993, pp. 630-650.
\end{thebibliography}
