\begin{thebibliography}{99}
\bibitem{RBA} Ash, Robert B. Basic probability theory. Courier Corporation, 2008.

\bibitem{Asmussen} Asmussen, S. (1987). \textit{Applied Probability and Queues}. John Wiley and Sons.

\bibitem{Bhat} Bhat, N. (2008). \textit{An Introduction to Queueing Theory: Modelling and Analysis in Applications}. Birkhauser.

\bibitem{Borovkov} Borovkov, A. A., and Schassberger, R. (1995). Ergodicity of a Polling Network. \textit{Stochastic Processes and their Applications}, 50(2), 253-262.

\bibitem{Daley68} Daley, D. J. (1968). The Correlation Structure of the Output Process of Some Single Server Queueing Systems. \textit{The Annals of Mathematical Statistics}, 39(3), 1007-1019.

\bibitem{Davis} Davis, M. H. A. (1984). Piecewise Deterministic Markov Processes: A General Class of Nondiffusion Stochastic Models. \textit{Journal of the Royal Statistical Society, Series B}, 46(3), 353-388.

\bibitem{Disney} Disney, R. L., Farrell, R. L., and Morais, P. R. (1973). A Characterization of $M/G/1$ Queues with Renewal Departure Processes. \textit{Management Science}, 19(11), Theory Series, 1222-1228.

\bibitem{Douc} Douc, R., Jacob, P. E., Lee, A., and Vats, D. (2022). Solving the Poisson equation using coupled Markov chains. arXiv preprint arXiv:2206.05691.

\bibitem{Getoor} Getoor, R. K. (1979). Transience and Recurrence of Markov Processes. In J. Azema and M. Yor (Eds.), \textit{Seminaire de Probabilités XIV} (pp. 397-409). New York: Springer-Verlag.

\bibitem{Gut} Gut, A. (1995). \textit{Stopped Random Walks: Limit Theorems and Applications}. Applied Probability.

\bibitem{HookHee} Ng, C. H., and Soong, B. H. (2008). \textit{Queueing Modelling Fundamentals with Applications in Communications Networks}. John Wiley and Sons.

\bibitem{Kleinrock} Kleinrock, L. (1975). \textit{Queueing Systems: Theory, Volume 1}. Wiley-Interscience.

\bibitem{Lang} Lang, S. (1973). \textit{Calculus of Several Variables}. Addison-Wesley Publishing Company.

\bibitem{MeynTweedie2} Meyn, S. P., and Tweedie, R. L. (1993). \textit{Markov Chains and Stochastic Stability}. Springer-Verlag.

\bibitem{Morozov} Morozov, E., and Steyaert, B. (2021). Stability analysis of regenerative queueing models. Springer International Publishing.

\bibitem{Portman} Portmann, C., and Renner, R. (2022). Security in quantum cryptography. \textit{Reviews of Modern Physics}, 94(2), 025008.

\bibitem{Ross} Ross, S. M. (2014). \textit{Introduction to Probability and Statistics for Engineers and Scientists}. Academic Press.

\bibitem{Serfozo} Serfozo, R. (2009). \textit{Basics of Applied Stochastic Processes}. Springer-Verlag.

\bibitem{Sharpe} Sharpe, M. (1998). \textit{General Theory of Markov Processes}. Academic.

\bibitem{Sigman2} Sigman, K., Thorisson, H., and Wolff, R. W. (1994). A Note on the Existence of Regeneration Times. \textit{Journal of Applied Probability}, 31, 1116-1122.

\bibitem{Stidham} Stidham, S. Jr. (1972). Regenerative Processes in the Theory of Queues, with Applications to the Alternating Priority Queue. \textit{Advances in Applied Probability}, 4(3), 542-577.

\bibitem{Thorisson} Thorisson, H. (2000). \textit{Coupling, Stationarity, and Regeneration}. Probability and its Applications. Springer-Verlag.

\bibitem{Xu} Xu, K., Fjelde, T. E., Sutton, C., and Ge, H. (2021, March). Couplings for Multinomial Hamiltonian Monte Carlo. In \textit{International Conference on Artificial Intelligence and Statistics} (pp. 3646-3654). PMLR.

\end{thebibliography}
